manuscript_one

### 2024-02-06 manuscript_one.Rmd
more table edits

library(RColorBrewer)
library(caret)
library(ggpubr)
library(rcompanion)
library(magrittr)
library(magick)
library(patchwork)
library(kableExtra)
library(webshot2)
library(devtools)
source("my_functions.R")
setup_libs()

@@

### i) Dataframe
```{r}
#create a dataframe with the with the data for the prevalence, density, and intensity values generated throughout the markdown  
table_one = data.frame(
  "Species" = c(rep("C. anthonyi", 2), rep("C. productus", 2), rep("C. anntenarius", 2)), 
  "Sex" = c("Females", "Males", "Females", "Males", "Females", "Males"),
  "Prevalence Infested" = c("100% <br> (n = 55)", "83% <br> (n = 12)", "86% <br> (n = 7)", "80% <br> (n = 4)", "71%  <br> (n = 4)", "100% <br> (n = 8)"),
  "Prevalence with Adults in Egg Mass"= c("100% <br> (n = 55)", NA, "100% <br> (n = 4)", NA, "100% <br> (n = 2)", NA),
  "Mean Density of Nicothoid Eggs in 1000 Host Eggs" = c("241.5 ± 385.6 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in 1000 Host Eggs" = c("*63.6 ± 113.4 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Adults in 1000 Host Eggs" = c("3.8 ± 6.3 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Intensity of Larvae in Gill Chamber" = c("14282.9 ± 21755.7 <br> (n = 19)", "235.2 ± 373.3 <br> (n = 10)", "24 ± 31.7 <br> (n = 3)", "42 ± 59.2 <br> (n = 6)", "4608 ± 5578 <br> (n = 4)", "61.7 ± 34.2 <br> (n = 7)"))

@@

#create the table with kable
final_table_one <- table_one %>%
  kable(format = "html",
        html_font = "Times New Roman",
        #digits = 0,
        align = "c",
        escape = F) %>%
  kable_styling(bootstrap_options = c("striped","hold_position")) %>%
  column_spec(1, italic = T, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(2, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(4, extra_css = "border-bottom: 1px solid;") %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
  save_kable(file = "figures/final_table_one.png",
             zoom = 3)

>>>>

library(RColorBrewer)
library(caret)
library(ggpubr)
library(rcompanion)
library(magrittr)
library(magick)
library(patchwork)
library(kableExtra)
library(magick)
library(webshot2)
library(devtools)
source("my_functions.R")
setup_libs()

@@

### i) Dataframe
```{r}
#create a dataframe with the with the data for the prevalence, density, and intensity values generated throughout the markdown  
table_one = data.frame(
  "Species" = c(rep("C. anthonyi", 2), rep("C. productus", 2), rep("C. anntenarius", 2)), 
  "Sex" = c("Females", "Males", "Females", "Males", "Females", "Males"),
  "Prevalence Infested" = c("100% <br> (n = 55)", "83% <br> (n = 12)", "86% <br> (n = 7)", "80% <br> (n = 4)", "71%  <br> (n = 4)", "100% <br> (n = 8)"),
  "Prevalence with Adults in Egg Mass"= c("100% <br> (n = 55)", NA, "100% <br> (n = 4)", NA, "100% <br> (n = 2)", NA),
  "Mean Density of Nicothoid Eggs in 1000 Host Eggs" = c("241.5 ± 385.6 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Density of Larvae in 1000 Host Eggs" = c("*63.6 ± 113.4 <br> (n = 27)", NA, NA, NA, NA, NA),
  "Mean Density of Adults in 1000 Host Eggs" = c("3.8 ± 6.3 <br> (n = 41)", NA, NA, NA, NA, NA),
  "Mean Intensity of Larvae in Gill Chamber" = c("14282.9 ± 21755.7 <br> (n = 19)", "196 ± 349 <br> (n = 12)", "24 ± 31.7 <br> (n = 3)", "64 ± 63 <br> (n = 4)", "4608 ± 5578 <br> (n = 4)", "61.7 ± 34.2 <br> (n = 7)"))

@@

#create the table with kable
final_table_one <- table_one %>%
  kable(format = "html",
        html_font = "Times New Roman",
        xdigits = 0,
        align = "c",
        escape = F) %>%
  column_spec(1, italic = T, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(2, extra_css = "border-bottom: 1px solid;") %>%
  row_spec(4, extra_css = "border-bottom: 1px solid;") %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  kable_styling(bootstrap_options = c("striped","hold_position")) %>%
  kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
  save_kable(file = "figures/final_table_one.png",
             zoom = 3)
